---
title: "Data Import"
output: github_document
---

```{r setup}
library(tidyverse)
```

To insert a code chunk, can press "option command i". The code chunk above is called "r setup"

## Read in some data
*A relative vs. absolute path*: A relative path example: tell it to go to the data file then find the FAS_litters.csv. An absolute path example: tell it to go to hard drive, then to users folder, then etc... Recommend use relative; they're stable

Read in the litters dataset.
```{r}
litters_df = read_csv("./data/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
#overwrite the original "litters_df" in line 18. load the clean_name function which is in the janitor package. Can load janitor package with tidyverse above but we only want the clean_name function so we write it with the ::. Running it basically changes the variable names (ex. "GD of Birth" to "gd_of_birth") in snake case.
```
"read_csv()" function exist in the reader package. Insert the relative path in the bracket. "." means from the starting point, go to data folder, and look at the FAS_litters csv file.

## Take a look at the data


```{r}
litters_df
#can show us that the dataset includes 49 rows and 8 columns
#"<chr>" means character variable
#"<dbl>" means "double," which is a particular kind of number; numeric variable
```

Printing in the console.
```{r}
head(litters_df)
#Gives us first 6 rows. Instead of "head" can also put "tail" to look at the last few rows.
```

```{r}
skimr::skim(litters_df)
#skimr package only has the "skim" function
#tells you how many are missing, min, max, white spaces, etc in character variables
#also tells you missing, mean, sd, quartile, histogram for numeric variables
```

Enter "view(litters_df)" in the console, instead of as a code chunk, will open a window for me to interact with the whole dataset. This avoids making the knitting process of R Markdown more difficult

## Options to read_csv
Comma separated values (CSV). 
"?read_csv" in the console gives more info. It shows how you can make it more specified with code

```{r}
litters_df = read_csv("./data/FAS_litters.csv", skip = 10, col_names = FALSE)
#"skip = " tells it how many rows to skip. Run "litters_df" to see if properly skipped. Add "col_names = FALSE" if skipping it messed up the top row.
```

```{r}
litters_df = read_csv("./data/FAS_litters.csv", na = c("", ".", "NA", 999))
#"every time it sees , or NA or 999, it will treat that as missing 
```

