---
title: "Data Import"
output: github_document
---

```{r setup}
library(tidyverse)
library(readxl)
library(haven)
```

To insert a code chunk, can press "option command i". The code chunk above is called "r setup"

## Read in some data
*A relative vs. absolute path*: A relative path example: tell it to go to the data file then find the FAS_litters.csv. An absolute path example: tell it to go to hard drive, then to users folder, then etc... Recommend use relative; they're stable

Read in the litters dataset.
```{r}
litters_df = read_csv("./data/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
#overwrite the original "litters_df" in line 18. load the clean_name function which is in the janitor package. Can load janitor package with tidyverse above but we only want the clean_name function so we write it with the ::. Running it basically changes the variable names (ex. "GD of Birth" to "gd_of_birth") in snake case.
```
"read_csv()" function exist in the reader package. Insert the relative path in the bracket. "." means from the starting point, go to data folder, and look at the FAS_litters csv file.

## Take a look at the data

```{r}
litters_df
#can show us that the dataset includes 49 rows and 8 columns
#"<chr>" means character variable
#"<dbl>" means "double," which is a particular kind of number; numeric variable
```

Printing in the console.
```{r}
head(litters_df)
#Gives us first 6 rows. Instead of "head" can also put "tail" to look at the last few rows.
```

```{r}
skimr::skim(litters_df)
#skimr package only has the "skim" function
#tells you how many are missing, min, max, white spaces, etc in character variables
#also tells you missing, mean, sd, quartile, histogram for numeric variables
```

Enter "view(litters_df)" in the console, instead of as a code chunk, will open a window for me to interact with the whole dataset. This avoids making the knitting process of R Markdown more difficult

## Options to read_csv
Comma separated values (CSV). 
"?read_csv" in the console gives more info. It shows how you can make it more specified with code

```{r}
litters_df = read_csv("./data/FAS_litters.csv", skip = 10, col_names = FALSE)
#"skip = " tells it how many rows to skip. Run "litters_df" to see if properly skipped. Add "col_names = FALSE" if skipping it messed up the top row.
```

Another example:
```{r}
litters_df = 
  read_csv(
    file = "data/FAS_litters.csv",
    col_names = FALSE,
    skip = 1
  )
```


```{r}
litters_df = read_csv("./data/FAS_litters.csv", na = c("", ".", "NA", 999))
#"every time it sees , or NA or 999, it will treat that as missing 
```

## Reading excel files

Remember to load "library(readxl)" beforehand
```{r}
mlb_df = read_excel("./data/mlb11.xlsx", range = "A1:F7")
#check by running "mlb_df" to check the format and see if you need to use janitor/clean_names to clean anything. Can also view the dataset by running "view(mlb_df)" in console.
```
Look at "?read_excel" for more info and how to make the code more specific and examples

## Reading SAS files

Remember to load "library(haven)" beforehand
```{r}
pulse_df = read_sas("./data/public_pulse_data.sas7bdat")
#check by running "pulse_df" to check the format, rows, columns, etc
```

## Comparison with Base R

What about `read.csv`...? DON'T use this. Instead USE `read_csv` because....
```{r}
litters_base = read.csv("data/FAS_litters.csv")
litters_readr = read_csv("data/FAS_litters.csv")

litters_base #prints out more information/entire dataset 
litters_readr #easier to read than "litters_base"
```

## Exporting data

Export the mlb sub-table (6x6 table after restriction in line 67).

```{r}
write_csv(mlb_df, "./data/mlb_subtable.csv")
#write_csv(what to export, path with name )
```


```{r}
litters_Df = 
  read.csv(
    file = "data/FAS_litters.csv",
    na = c("NA", "", "."), 
    col_types = cols(
      Group = col_factor()
    )
  )
```


